What is happening on Twitter? A framework for student research projects with tweets

### 2020-09-16 Rmd/jse-special-issue-2020-october.Rmd
added text about Box 1976

@@

To illustrate the value of Twitter data, we present below a 
reproducible case study. It is essentially a reproduction of our second student's project, but at a 
distinct time period. In it, we aim to detect a social media 
event by examining topic content over time. We use Latent Dirichlet 
Allocation (LDA) models [@blei2003latent] to infer topics on three consecutive days centered 
on Memorial Day 2020. We chose this example case study, 
instead of the student projects, because of limited data 
availability for the student projects. Despite this, the case study 
illustrates the strategy and methods for one student 
project.

We next discuss case study design, tweet collection, and tweet structure, before turning 
to statistical methods for the case study.

>>>>

Through our work with tweets, we demonstrate
that Twitter data is a rich source of new data science research questions. 
@box1976science described a 
positive feedback loop for the interplay of discipline-specific research
and quantitative methods research. The two components, "science" and "statistics" in the 
language of @box1976science, iteratively fuel research questions in each other. 
A new statistical 
method enables new discipline-specific questions to be addressed, while a new 
scientific question motivates new data science methods. We describe below two
data science research questions that mentored students addressed with tweets.

@@

To illustrate the value of Twitter data and to encourage readers to envision other uses for tweets, we present below a 
reproducible case study. It is essentially a reproduction of our second student's project, but at a 
distinct time period. In it, we aim to detect a social media 
event by examining tweet topic content over time. We use Latent Dirichlet 
Allocation (LDA) models [@blei2003latent] to infer topics on three consecutive days centered 
on Memorial Day 2020. We chose this example case study, 
instead of the student projects, because of limited data 
availability for the student projects. Despite this, the case study 
illustrates the strategy and methods for one student 
project. Below, we discuss case study design, tweet collection, and tweet structure, 
before turning to statistical methods for the case study.
